Mixed-Effects Model for MTLD by Gender

### 2018-08-17 paper.Rmd
don't show warning in color counts

```{r join-colors-and-tokens, echo = TRUE}
count_estimates <- color_counts %>%
  left_join(parents) %>%
  mutate(age_months = target_child_age,
         age_bin = as.integer(floor(age_months / 6) * 6),
         color = tolower(gloss)) %>%
  group_by(age_bin, color, target_child_id, transcript_id) %>%
  summarise(count = sum(count), num_tokens = sum(num_tokens)) %>%
  summarise(count = sum(count), num_tokens = sum(num_tokens)) %>%  
  mutate(parts = count / num_tokens * 1e6)
```

>>>>

```{r join-colors-and-tokens, echo = TRUE, warning=F}
count_estimates <- color_counts %>%
  left_join(parents) %>%
  mutate(age_months = target_child_age,
         age_bin = as.integer(floor(age_months / 6) * 6),
         color = tolower(gloss)) %>%
  group_by(age_bin, color, target_child_id, transcript_id) %>%
  summarise(count = sum(count), num_tokens = sum(num_tokens)) %>%
  summarise(count = sum(count), num_tokens = sum(num_tokens)) %>%  
  mutate(parts = count / num_tokens * 1e6)
```
